---
title: "My Package Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My Package Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753SAVA24)
```

# Function 1

The first function I will be showcasing will be the myncurve function. I will just be using predefined numbers as a data set is not needed for this function:

```{r}
myncurve(5, 10, 2)
```

# Function 2

The next function I will be using is the myclt function and is a function used to visualize the central limit theorem. I will once again be using predefined values:

```{r}
myclt(n=10,iter=10000)
```

# Function 3

The next function I will be showcasing is the myboot2 function. This function performs a bootstrap operation from a sample and produces a graph along with general results from the function.

```{r}
sam = c(1,1,1,2,2,2,2,3,3,3,4,4)
myboot2(x = sam, fun = "median")
```

# Function 4

The last function I will showcase is the function I made for project 1, ntickets. It determines the number of seats an airline should sell depending on the likelihood of someone showing up and the number of seats on a plane.

```{r}
ntickets(N=400, gamma=0.02, p=0.95)
```

